Paper Plots V2

### 2025-03-31 Rmd/paper_plots/paper_plots_1.3.Rmd
add paper runs and plots

out_3.2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_1.4_ISS_500iters_output_2025-03-06.RDS") ### mislabeled

@@

@@

@@

### * 2003 and 2004 histograms
```{r, fig.height=8, fig.width=9}

out_1.4$length$og_props %>% 
  tidytable::filter(YEAR %in% 2003:2004) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

@@

p3 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity") +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "B") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_1.4$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 300), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000))

p1 / p3

@@

@@

# all years
ggplot(data = df2, aes(x = year, y = ISS, group = scenario, colour = scenario)) +
  geom_line() +
  labs(x = "", y = "ISSB") +
  geom_point() + 
  theme_classic() +
  theme(legend.position = c(0.84, 0.8),
        axis.title.x = element_blank())

# 1999:2023
df2 %>% 
  filter(year%in%1999:2023) -> df2
ggplot(data = df2, aes(x = year, y = ISS, group = scenario, colour = scenario)) +
  geom_line() +
  labs(x = "", y = "ISSB") +
  geom_point() + 
  theme_classic() +
  theme(legend.position = c(0.84, 0.8),
        axis.title.x = element_blank())
```

@@

```{r, fig.height=8}
### plots

@@

@@

>>>>

out_3.2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_3.2_ISS_500iters_output_2025-03-07.RDS") ### mislabeled

@@

# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
# par(mfrow = c(3,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
par(mfrow = c(2,1), mar = c(0,3.1,0,0), oma = c(3, 0, 2, .5), mgp = c(2, .6, 0))
plot(out_1.4$length$iss$YEAR, out_1.4$length$iss$iss, type = "l", ylab = "ISS", xaxt = "n", ylim = c(0, 15000), cex.lab = 1.3) 
lines(assessment_2023_iss$year, assessment_2023_iss$iss, col = "blue")
lines(out_1.4$length$iss$YEAR, out_1.4$length$iss$nhls, col = "red")
legend(1977, 11000, lty = c(1,1,1,1), col = c("black", "blue", "red"), legend = c("ISSB", "ISSA", "number of hauls"), bty = "n")
text(1977, 14000, "A")

plot(out_1.4$length$iss$YEAR, out_1.4$length$iss$nss, type = "l", ylab = "Nominal Sample Size", xlab = "Year", cex.lab = 1.3) 
text(1977, 420000, "B")
mtext("Year", side = 1, line = 2, cex = 2)

### * Time series 2 panel no-SS

@@

## histogram test, which are similar? 
provide a counter example to 2003:2004

out_1.4$length$og_props %>% 
  tidytable::filter(YEAR %in% 1997:1998) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p1

@@

### * 2003 and 2004 histograms
```{r, fig.height=8, fig.width=9}
out_1.4$length$og_props %>% 
  tidytable::filter(YEAR %in% 2003:2004) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

@@

p3 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "F") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_1.4$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 75), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
                     limits = c(0, 35000),
                     expand = c(0, 0))

# now do RSS with boot_length only.
out_5.2$length$rss %>% 
  tidytable::filter(YEAR %in% 2003:2004) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p3.2 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "B") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_5.2$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 110), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
                     limits = c(0, 35000),
                     expand = c(0, 0))

# now do RSS with boot_length and boot_haul.
out_9.2$length$rss %>% 
  tidytable::filter(YEAR %in% 2003:2004) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p3.3 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "C") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_9.2$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 75), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
                     limits = c(0, 35000),
                     expand = c(0, 0))

# now do RSS with boot all.
out_4.2$length$rss %>% 
  tidytable::filter(YEAR %in% 2003:2004) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p3.4 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "D") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_4.2$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 30), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
                     limits = c(0, 35000),
                     expand = c(0, 0))

# now do RSS with boot all + SS
out_2.2$length$rss %>% 
  tidytable::filter(YEAR %in% 2003:2004) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p3.5 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "E") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_2.2$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 30), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
                     limits = c(0, 35000),
                     expand = c(0, 0))

p1 / p3
p1 / p3 / p3.2
```

```{r, fig.height=10}
p1 / p3.2 / p3.3 / p3.4 / p3.5 / p3

@@

### with another year

#### histograms
```{r, fig.height=10}
out_1.4$length$og_props %>% 
  tidytable::filter(YEAR %in% 2021:2022) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

# now do RSS
out_1.4$length$rss %>% 
  tidytable::filter(YEAR %in% 2021:2022) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p3 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "F") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_1.4$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 75), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
                     limits = c(0, 35000),
                     expand = c(0, 0))

# now do RSS with boot_length only.
out_5.2$length$rss %>% 
  tidytable::filter(YEAR %in% 2021:2022) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p3.2 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "B") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_5.2$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 110), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
                     limits = c(0, 35000),
                     expand = c(0, 0))

# now do RSS with boot_length and boot_haul.
out_9.2$length$rss %>% 
  tidytable::filter(YEAR %in% 2021:2022) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p3.3 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "C") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_9.2$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 75), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
                     limits = c(0, 35000),
                     expand = c(0, 0))

# now do RSS with boot all.
out_4.2$length$rss %>% 
  tidytable::filter(YEAR %in% 2021:2022) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p3.4 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "D") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_4.2$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 30), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
                     limits = c(0, 35000),
                     expand = c(0, 0))

# now do RSS with boot all + SS
out_2.2$length$rss %>% 
  tidytable::filter(YEAR %in% 2021:2022) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p3.5 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 200) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "E") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_2.2$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 30), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 35000, by = 2500),
                     labels = c(0, "", 5000, "", 10000, "", 15000, "", 20000, "", 25000, "", 30000, "", 35000),
                     limits = c(0, 35000),
                     expand = c(0, 0))

# p1 / p3
# p1 / p3 / p3.2

p1 / p3.2 / p3.3 / p3.4 / p3.5 / p3

### with another year

#### histograms
```{r, fig.height=10}
out_1.4$length$og_props %>% 
  tidytable::filter(YEAR %in% 1997:1998) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

# now do RSS
out_1.4$length$rss %>% 
  tidytable::filter(YEAR %in% 1997:1998) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p3 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 20) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "F") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_1.4$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 75), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 3000, by = 250),
                     limits = c(0, 3000),
                     expand = c(0, 0))

# now do RSS with boot_length only.
out_5.2$length$rss %>% 
  tidytable::filter(YEAR %in% 1997:1998) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p3.2 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 10) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "B") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_5.2$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 110), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 3000, by = 250),
                     limits = c(0, 3000),
                     expand = c(0, 0))

# now do RSS with boot_length and boot_haul.
out_9.2$length$rss %>% 
  tidytable::filter(YEAR %in% 1997:1998) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p3.3 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 10) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "C") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_9.2$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 75), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 3000, by = 250),
                     limits = c(0, 3000),
                     expand = c(0, 0))

# now do RSS with boot all.
out_4.2$length$rss %>% 
  tidytable::filter(YEAR %in% 1997:1998) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p3.4 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 10) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "D") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_4.2$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 30), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 3000, by = 250),
                     limits = c(0, 3000),
                     expand = c(0, 0))

# now do RSS with boot all + SS
out_2.2$length$rss %>% 
  tidytable::filter(YEAR %in% 1997:1998) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

p3.5 = ggplot(data = props.sub, aes(x = rss, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity", binwidth = 10) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Count", tag = "E") + 
  geom_point(data = props.sub %>% 
               tidytable::left_join(out_2.2$length$iss %>% 
                                      tidytable::select(YEAR, iss)) %>% 
               tidytable::summarise(x = unique(iss), .by = Year) %>% 
               # tidytable::summarise(x = median(rss), .by = Year) %>% 
               tidytable::mutate(y = c(9,9)), aes(x,y, fill = Year), shape = 25, size = 4, color = "black") +
  scale_y_continuous(limits = c(0, 30), expand = c(0, 0)) +
  # scale_x_continuous(n.breaks = 8)
  scale_x_continuous(breaks = seq(0, 3000, by = 250),
                     limits = c(0, 3000),
                     expand = c(0, 0))

# p1 / p3
# p1 / p3 / p3.2

p1 / p3.2 / p3.3 / p3.4 / p3.5 / p3

# For presentation
```{r, fig.height=10}
out_1.4$length$og_props %>% 
  tidytable::filter(YEAR %in% 1997) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> props.sub

ggplot(data = props.sub, aes(x = LENGTH, y = og_FREQ, colour = Year)) +
  geom_line() +
  geom_area(aes(fill = Year, group = Year), alpha = 0.5, position = "identity") +
  theme_classic() +
  scale_x_continuous(limits = c(22, 108),
                     n.breaks = 9) +
  labs(x = "Length Bin-b (cm)", y = "Proportion (P)", tag = "") +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  scale_y_continuous(limits = c(0, .032), expand = c(0, 0)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

out_1.4$length$iss$nss[out_1.4$length$iss$YEAR==1997]
```

@@

# all years
ggplot(data = df2, aes(x = year, y = ISS, group = scenario, colour = scenario)) +
  geom_line() +
  labs(x = "", y = "ISSB") +
  geom_point() + 
  theme_classic() +
  theme(legend.position = c(0.84, 0.8),
        axis.title.x = element_blank())
```

```{r, fig.width=9, fig.height=5}
# 1999:2023
df2 %>% 
  filter(year%in%1999:2023) %>% 
ggplot(aes(x = year, y = ISS, group = scenario, colour = scenario)) +
  geom_line() +
  geom_point() +
  scale_shape_manual(values = c(1,2,3)) +
  labs(x = "Year", y = "ISSB", color = "Expansion Complexity") +
  scale_color_manual(labels = c("None", "Medium: haul only", "Full: haul, area, gear, month"), values = c("blue", "red", "black")) +
  geom_point() + 
  theme_classic() + 
  theme(legend.position = c(0.7, 0.9),
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 14))
```

@@

```{r, fig.height=6}
### plots

@@

## for presentation
df4.a %>%
  filter(type=="relative_N") %>% 
  ggplot(aes(x = scenario, y = ISS.error)) +
  geom_boxplot(aes(fill = type)) +
  labs(x = "Adjusted Samples Per Haul", y = "ISSB % Difference", tag = "") +
  theme_classic() +
  theme(legend.position = c(3, 0.15),
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 14)) + 
  guides(fill = guide_legend(title = "relative to baseline")) +
  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
  # geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-80, 10))

@@

# * Steve's data

a.out = read.csv("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/Fishery ISS Paper/from Steve B/Derived_quants.csv")
p.out = read.csv("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/Fishery ISS Paper/from Steve B/parameters.csv")

a.out %>% glimpse()

SSB.names = paste0("SSB_", 1977:2038)
SPRratio.names = paste0("SPRratio_", 1977:2038)
Bratio.names = paste0("Bratio_", 1977:2038)

SSB = a.out %>% 
  tidytable::filter(MODEL2 == "OM tuned", Label%in%SSB.names) %>% 
  tidytable::bind_rows(a.out %>% 
                         tidytable::filter(MODEL2 == "Fiss tuned", Label%in%SSB.names)) %>% 
  tidytable::mutate(Year = as.numeric(substr(Label, 5, 8)))
SPRratio = a.out %>% 
  tidytable::filter(MODEL2 == "OM tuned", Label%in%SPRratio.names) %>% 
  tidytable::bind_rows(a.out %>% 
                         tidytable::filter(MODEL2 == "Fiss tuned", Label%in%SPRratio.names)) %>% 
  tidytable::mutate(Year = as.numeric(substr(Label, 10, 13)))
Bratio = a.out %>% 
  tidytable::filter(MODEL2 == "OM tuned", Label%in%Bratio.names) %>% 
  tidytable::bind_rows(a.out %>% 
                         tidytable::filter(MODEL2 == "Fiss tuned", Label%in%Bratio.names)) %>% 
  tidytable::mutate(Year = as.numeric(substr(Label, 8, 11)))

SSB %>% 
  tidytable::rename(Model_run = MODEL2) %>% 
  ggplot(aes(x = Year, y = Value, ymin = LO, ymax = HI, fill = Model_run, linetype = Model_run)) +
  geom_line() +
  geom_ribbon(alpha = 0.5) +
  xlab("Year") + 
  ylab("SSB") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.85), 
        legend.direction = "vertical", 
        legend.box = "vertical") +
  geom_vline(xintercept = 2023, linetype = "dashed", color = "black") +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

SPRratio %>% 
  ggplot(aes(x = Year, y = Value, ymin = LO, ymax = HI, fill = MODEL2, linetype = MODEL2)) +
  geom_line() +
  geom_ribbon(alpha = 0.5) +
  xlab("Year") + 
  ylab("SPRratio") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.3), 
        legend.direction = "vertical", 
        legend.box = "vertical") +
  geom_vline(xintercept = 2023, linetype = "dashed", color = "black")
Bratio %>% 
  ggplot(aes(x = Year, y = Value, ymin = LO, ymax = HI, fill = MODEL2, linetype = MODEL2)) +
  geom_line() +
  geom_ribbon(alpha = 0.5) +
  xlab("Year") + 
  ylab("Bratio") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.85), 
        legend.direction = "vertical", 
        legend.box = "vertical") +
  geom_vline(xintercept = 2023, linetype = "dashed", color = "black")

# Tables of parameters

p.out %>% 
  tidytable::filter(Label%in%c("VonBert_K_Fem_GP_1", "L_at_Amax_Fem_GP_1", "SR_LN(R0)"),
                    MODEL2%in%c("OM tuned", "Fiss tuned")) %>% 
  tidytable::mutate(StdDev = Parm_StDev) %>% 
  tidytable::select(-Parm_StDev) %>% 
  tidytable::bind_rows(a.out %>% 
                         tidytable::filter(Label%in%c("SSB_2023", "SSB_2038", "Bratio_2023", "Bratio_2038", "SPRratio_2023", "SPRratio_2038"),
                                           MODEL2%in%c("OM tuned", "Fiss tuned"))) %>% 
  tidytable::select(-X, -MODEL, -HI, -LO) -> p.table

require(xtable)
age <- sample(c('30-50', '50-70', '70+'), 200, replace=T)
sex <- sample(c('Male', 'Female'), 200, replace=T)
val <- table(age, sex)
val <- rbind(val, formatC(prop.table(val)*100, format='f', digits=1))
val <- structure(val, dim=c(3, 4))
val <- rbind(c('n', '%'), val)
rownames(val) <- c('', sort(unique(age)))
val <- xtable(val)

addtorow <- list()
addtorow$pos <- list(0)
addtorow$command <- paste0(paste0('& \\multicolumn{2}{c}{', sort(unique(sex)), '}', collapse=''), '\\\\')

print(val, add.to.row=addtorow, include.colnames=F)
